%-------------------------
% Resume in Latex
% Author : Michael Makhool
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\usepackage{enumitem}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemWithDate}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeSubheadingDuo}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-15pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemSummaryStart}{\begin{itemize}[label={},leftmargin=*]}
\newcommand{\resumeItemSummaryEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Michael Makhool} \\ \vspace{1pt}
    \small 313-418-6902 $|$ \href{mailto:mmakhool6@gmail.com}{\underline{mmakhool6@gmail.com}} $|$ 
    \href{https://linkedin.com/in/mickmakhool}{\underline{linkedin.com/in/mickmakhool}} $|$
    \href{https://github.com/mmakhool/portfolio}{\underline{github.com/mmakhool/portfolio}} $|$
    \small Detroit, MI
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{C\#, .NET Framework, .NET MAUI, ASP.NET, ASP.NET Core, Blazor}
    \resumeItem{JavaScript, TypeScript, Node.js, Nest.js, Express, Angular, AngularJS, Svelte}
    \resumeItem{Progress ABL, Telerik, Kendo UI, OpenEdge, PDSOE, Sonic ESB, SonicMQ}
    \resumeItem{Jest, Test Driven Development (TDD), Postman, Unit Testing, Integration Testing, End-to-End Testing}
    \resumeItem{RESTful API, Swagger, OAuth2 Authentication}
    \resumeItem{CSS/HTML, React, Vue, CSS Tailwinds}
    \resumeItem{Amazon Web Services (AWS), Lambda, SQS, SNS, S3, EC2, Terraform}
    \resumeItem{MongoDB, MongoDB Compass, Mongosh}
    \resumeItem{SQL Server, MySQL, PostgreSQL}
    \resumeItem{CircleCI, SonarQube, Jenkins, Docker, Kubernetes}
    \resumeItem{Agile, Scrum, Kanban, Azure DevOps}
    \resumeItem{Visual Studio 2022, Visual Studio Code, Git, GitHub Actions, Lucidchart}
  \resumeItemListEnd

\section{Additional Skills}
  \resumeItemListStart
    \resumeItem{Full-stack programming with experience in app development at multiple scales}
    \resumeItem{Agile focused with an impactful presence in stand-ups, sprint planning, and retrospectives}
    \resumeItem{Ability to learn and implement unfamiliar methodologies and technologies quickly}
    \resumeItem{Highly research oriented with a passion for learning new technologies}
    \resumeItem{Mentoring of junior developers and interns}
    \resumeItem{Professional development focused, driven to grow and understand best practices}
    \resumeItem{Strong communication skills with a focus on collaboration and team building}
    \resumeItem{Former 91B (Wheeled Vehicle Mechanic) Specialist in the United States Army}
    \resumeItem{Professional level video game player (self-proclaimed)}
  \resumeItemListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheadingDuo
      {\textbf{Coe Press Equipment} $|$ \emph{Sterling Heights, MI}}{Nov. 2023 -- present }
      \resumeItemSummaryStart
        \resumeItemWithDate
          {\textbf{CoeDashboard}}{IT Developer -- Nov. 2023 - present}
            {Upon joining, I identified an outdated time-clock system in our backlog and initiated its modernization. I designed a scalable dashboard application, 
            starting with a MongoDB database schema based on existing Progress OpenEdge tables. Initially a MERN stack application, we transitioned to C\# and .NET MAUI 
            with the addition of a new developer. I implemented MVVM architectures, dependency injection, developed REST APIs and established CI/CD pipelines in 
            GitHub Actions for deployment and versioning. We release weekly updates for feature additions and bug fixes, anticipating significant impact from the application.}
        \resumeItemWithDate
          {\textbf{Journey}}{Nov. 2023 - present}
            {I maintain and update Progress OpenEdge applications, mentor new developers, and shadow users biweekly to understand their workflows and identify UX improvements. 
            I reformatted a sales tracking GUI called Journey. Following user feedback, I restructured the GUI, proposed database schema changes, and tested the changes to 
            ensure the changes compiled with the existing code. Implementation of these changes has caused an increase in usage with the sales team and has allowed them 
            to manage their CRM data quicker and more efficiently.}
      \resumeItemSummaryEnd
    \resumeSubheadingDuo
      {\textbf{Rocket Mortgage / Quicken Loans} $|$ \emph{Detroit, MI}}{Nov. 2017 -- Aug. 2023 }
      \resumeItemSummaryStart
        \resumeItemWithDate
          {\textbf{Support Toolbox}}{Software Engineer -- Oct. 2022 - Aug. 2023}
            {Developed an Angular/TypeScript application based off of an existing app shell created by another engineering team. The goal was to create a toolbox to house on-demand
            loan-level fixes for trending issues, enabling Tier 1 support teams to avoid potential escalation times, while reducing the load on Tier 2 and Tier 3 teams
            by managing ticket intake more effectively at the Tier 1 level. I created the backend for frontend services and controllers, set up connections to oAuth and
            Amazon SQS, and developed a tool to resolve cross-platform mismatch errors. After release, there was a substantial reduction in overall OnCall escalations.}
        \resumeItemWithDate
          {\textbf{Login Metrics}}{Sept. 2022 - Oct. 2022}
            {The objective of this project was to develop a scheduled task program capable of retrieving login data. This program also supports ad hoc operations, 
            allowing users to input specific dates directly on the interface in each environment of the primary platform. This functionality is crucial for maintaining
            user-licensing compliance. To achieve this, I utilized an existing SOC Audit code table/driver to house the report generated by our scheduled task program.
            This program was developed in Progress ABL and JavaScript, and was integrated with Amazon S3 for data storage. After development, the program was 
            able to find areas of cost savings in relation to excess licensing of users that no longer needed that particular license.}
        \resumeItemWithDate
          {\textbf{Space Mountain}}{Apr. 2022 - Sept. 2022}
            {Embedded into a team that was responsible for the development and maintenance of all API endpoints for the primary mortgage platform. I made contributions
            to their QE testing suite by developing a BA tool that supported accurate county recording costs for clients in applicable counties. Additionally, I took the
            lead role on 3 different features, including an application made with JavaScript and Svelte that checked current AWS region statuses. I participated in weekly 
            office-hours sessions to assist developers from other teams seeking help with creating and integrating new endpoints, and I held code reviews within and outside
            of our team to ensure quality and consistency.}  
        \resumeItemWithDate
          {\textbf{Input Validation}}{Progress Developer -- Mar. 2022 - Apr. 2022}
            {I helped enhance the validation in our PUT, POST, and DELETE APIs before data is saved into the Progress database. I built input validation classes and created
            unit tests to verify the information being passed through, developed architecture diagrams, and documentation to support and reference the API validation process, 
            and coordinated with consumers of the API to conduct testing and confirm services are functioning as intended.}
        \resumeItemWithDate
          {\textbf{QuickClock}}{Feb. 2020 - Aug. 2023}
            {I took ownership of the time-clock system that handled all hourly employee time tracking. I enhanced the integration within the primary mortgage platform by
            reinforcing the procedures for user input validation and ensuring data integrity. Corrected various functionality issues that allowed for users to bypass the system's
            validation checks, and restructured existing documentation to allow for easier onboarding of future app owners.}
        \resumeItemWithDate
          {\textbf{xBert}}{Nov. 2019 - Mar. 2022}
            {Obtained ownership of the xBert application, a backend admin tool that manages the creation and maintenance of all customer user accounts within the primary mortgage platform.
            I made improvements to how the application handled logging by replacing the existing logging system with a more robust and efficient logging library. This change allowed
            for improved integration with up-to-date systems and provided a more detailed log output for debugging purposes.}
        \newpage    
        \resumeItemWithDate
          {\textbf{AMP Programming OnCall}}{Aug. 2018 - Aug. 2023}
            {I addressed areas of improvement in our existing OnCall process to senior leadership with a proposal to have our team take ownership of the OnCall Rotation. I was given
            the opportunity to transition into a trial developer role while continuously enhancing the process and flow for all loan-level escalation tickets. I streamlined the
            confusing process that was originally handled by engineers from multiple teams assigned to a rotation, and created a more efficient process that significantly reduced
            the time it took to resolve issues. Having the OnCall rotation operating by a single team working directly with each support tier caused escalation turn-times to drop from
            48 hours or more to less than 24 hours with a majority of escalations being resolved within 2-3 hours.}
        \resumeItemWithDate
          {\textbf{Knowledgebase Migration}}{Business Support Analyst -- Jan. 2018 - Jan. 2019}
            {I led the migration of all team knowledge base articles from a legacy system to a new in-house platform, improving accessibility and searchability.
            I analyzed usage data to identify trending articles, collaborated with other analysts to update and enhance the content, and established a new documentation standard 
            to ensure consistency and quality across all articles. This standard included guidelines for article structure, tagging, and formatting. Additionally, 
            I trained team members on the new platform and documentation standard, ensuring a smooth transition and continuous improvement in our knowledge management.}
        \resumeItemWithDate
          {\textbf{SE Shadowing}}{Nov. 2017 - Aug. 2018}
            {Utilized weekly professional development time provided by the company to shadow and work with software engineers within our stream to gain a better understanding of the technology
            stack that supports the primary mortgage application. I assisted in the development of loan-level procedural Progress fixes and queries while identifying process improvements
            and potential automation opportunities.}
      \resumeItemSummaryEnd
  \resumeSubHeadingListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%         {\textbf{CoeClock} $|$ \emph{C\#, .NET MAUI, MongoDB, Git}}{2023 -- 2024}
%         \resumeItemListStart
%           \resumeItem{Developed a modern and scalable dashboard and time-clock application using the .NET 8 framework, effectively replacing the existing legacy system}
%           \resumeItem{Utilized the multi-platform capabilities of .NET MAUI to seamlessly develop cross-platform applications, ensuring a consistent and unified user experience across various devices and operating systems}
%           \resumeItem{Created the dashboard with scalability in mind, allowing for future services to be implemented}
%           \resumeItem{Established a new MongoDB database to efficiently store and manage records previously housed in a SQL database}
%           \resumeItem{Seamlessly integrated the MongoDB database with the application, optimizing authentication, data retrieval, and enhancing overall system performance}
%         \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Support Toolbox} $|$ \emph{TypeScript, Angular, Node.js, AWS (S3, SQS, Lambda), CircleCI, Git}}{2023}
%           \resumeItemListStart
%             \resumeItem{Developed a full-stack application to support Tier 1 support tickets, reducing the load on Tier 2 and Tier 3 teams by creating tools to manage ticket intake at Tier 1 level}
%             \resumeItem{Adapted and learned new processes, including Terraform, Circle configs, bearer token authorization, and API connectors, to create the Toolbox UI and Backend for Frontend}
%             \resumeItem{Acquired proficiency in Angular, NodeJS, and TypeScript to align with the syntax of the existing Admin Shell}
%             \resumeItem{Led the development of the back end service and controller for a tool resolving cross-platform mismatch errors}
%             \resumeItem{Overcame challenges in SQS Queue Services development by conducting extensive research through online sources and AWS documentation, as there were limited in-house repositories utilizing SQS}
%           \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Login Metrics} $|$ \emph{Progress ABL, JavaScript, Amazon S3, CircleCI, Git}}{2022 -- 2023}
%           \resumeItemListStart
%             \resumeItem{Led the development of a Tidal Job program to streamline the acquisition of login data, ensuring user-licensing compliance across all environments}
%             \resumeItem{Leveraged an existing SOC Audit codetable/driver to contain the report executed by the Tidal Job, optimizing report generation and data retrieval processes}
%             \resumeItem{Enabled ad hoc execution of the program with customized date ranges for maximum flexibility and accuracy}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd

    %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {\textbf{Wayne State University} $|$ \emph{Detroit, MI}}{Jan. 2020 -- present }
    {In Progress}{BS in Computer Science - Junior - Overall GPA: 3.83}
  \resumeSubHeadingListEnd
\vspace{1mm}
%-------------------------------------------
\end{document}
